### 2020-03-26 papers.tex
Don't end document early

\insertmydocument{chapter}{TODO-TITLE}{Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascón-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
\insertmydocument{chapter}{TODO-TITLE}{Üzelgün}{pdfs/commentary/27longZemplen-C.doc.pdf}

>>>>

% \insertmydocument{chapter}{TODO-TITLE}{Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascón-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
% \insertmydocument{chapter}{TODO-TITLE}{Üzelgün}{pdfs/commentary/27longZemplen-C.doc.pdf}
